MCTS Applied to Co-operative Problems

### 2015-08-02 Report/ceec.tex
Fixed the issue with proves and indicates
Reworded the research problem

\section{Introduction}
\gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually. \gls{ggp} in real time video games is a popular competition \cite{perez2014}

@@

Figure \ref{1epairedTicks} shows the ability of each Agent to solve a simple path finding problem. The \emph{GAcontroller}, with its macro actions, is hindered by its inability to make single step moves and has trouble actually walking straight to the target. The \emph{VariGA} does significantly better, due to its ability to perform single step moves. Figure \ref{1pairedTicks} shows that most of the controllers really struggle when the \emph{Door} and \emph{Buttons} are added. This proves that the challenge of the task is high, although perhaps remarkable that \gls{mcts} is able to solve the tasks.

>>>>

\section{Introduction}
This research problem that this paper will asses is how \gls{ggp} agents perform when trying to solve a simple co-operative problem, with a focus on \gls{mcts}.

\gls{ggp} is the field of writing \gls{ai} agents that can play a multitude of games without being written specifically for each one individually. \gls{ggp} in real time video games is a popular competition \cite{perez2014}

@@

Figure \ref{1epairedTicks} shows the ability of each Agent to solve a simple path finding problem. The \emph{GAcontroller}, with its macro actions, is hindered by its inability to make single step moves and has trouble actually walking straight to the target. The \emph{VariGA} does significantly better, due to its ability to perform single step moves. Figure \ref{1pairedTicks} shows that most of the controllers really struggle when the \emph{Door} and \emph{Buttons} are added. This indicates that the challenge of the task is high, although perhaps remarkable that \gls{mcts} is able to solve the task.
